---
title: "Week 2: Foundational Skills"
subtitle: ""
author: "Joshua M. Rosenberg, Alex Lishinski"
date: "January 28, 2021"
output:
  xaringan::moon_reader:
    css: [theme.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
  

# Breakout rooms!

Starting with whomever had a snack or meal most recently, discuss . . . 

Based on X criteria
- What was one “win” you had from the homework?
- What was one challenge you had from the homework?

(10 minutes)

---

## Projects and Directories: Setting up your environment

Working Directories 

```{r}
getwd() 
```

R Projects 

Project options saved in .Rproj file

here package

```{r}
library(here)
# base project folder identified by here()
here() 
# data subfolder within base folder
here("data")
```

---

# Packages

1. What are packages? 
  + Code bundles that add functionality to R
1. Where do we get packages?
  + CRAN or github
1. How do we install packages?
  + install.packages("pkg-name")
1. How do we know what packages to use?
  + Searching 
  + CRAN task views
1. How do we use packages?
  + library("pkg-name")

---

## Data

Loading different types of data

.csv

```{r}
library(readr)
#readr::read_csv(here("data", "filename.csv"))
```
.xlsx

```{r}
library(readxl)
read_excel((here("data", "schedule.xlsx")))
```

.sav

```{r}
library(haven)
#read_sav((here("file-name.sav")))
```

---

## Functions

```{r}
library(dplyr)
#mtcars
glimpse(mtcars)
```

---

## Finding help

```{r}
?mean
?dplyr::filter
```

---

## Trying out a new function and working through challenges

---

# Basic programming operators

```{r}
mtcars %>% 
  
```

---

Assignment operator

```{r}
thing1 <- "text"
thing1
thing2 <- 2
thing2
thing3 <- c(1,2,3,4,5)
thing3
thing4 <- 4.5729
thing4
thing5 <- TRUE
thing5
```

---

Assignment operator


```{r}

```

---

# Basic programming operators

Math

```{r}
x <- 3 * 4
x
y <- 2 + 3 -1
y
z <- 4 / 2 ** 3
```

---

# Basic programming operators

Logic

```{r}
x <- TRUE
y <- FALSE
# and
x & y
# or 
x | y
# not 
!x
```


---

# Basic programming operators

Subsetting and accessing objects

```{r}
library(dplyr)
# cols by name
mtcars %>% 
  select(mpg, cyl, hp)

#mtcars
# variables in data frame or tibble
mtcars$mpg
mtcars$cyl
mtcrs$hp

# rows by index
mtcars[1:10,]
# rows by condition
dplyr::filter(mtcars, mpg < 20)
# cols by number
mtcars[,c(1,2,4)]

```

---

# Breakout rooms

```{r}
library(dplyr)

storms
```

Use `dplyr::select()`, `dplyr::filter()`, and `dplyr::arrange()`.

Create a new R Markdown document.

---

## Readings

Two assigned readings for the next week:

- Data Science in Education Using R (DSIEUR) chapter - Foundational skills: https://datascienceineducation.com/c06.html
- Grammar of Graphics: http://vita.had.co.nz/papers/layered-grammar.pdf

---

# Syllabus Discussion

1. Big project - topics, proposals 
1. Assignment details
1. Videos
1. Cleaning data
1. Social media / textual data / qualitative data

--- 

# Wrapping up

In your base group's Slack channel:

- What is one thing you took away from today?
- What is something you want to learn more about? 
