---
title: "HW Week 2 - Foundational Skills"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up your environment

Save this file to a directory where you will keep you work for the semester.

Associate that directory with an R project.

For more instructions on how to do that see video.

```{r}
rprojroot::has_file('.Rproj')
rprojroot::find_root(criterion = rprojroot::is_rstudio_project)
here::here()
```

## Read data

There is a file called answer_export.csv in the data folder here: https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed

Download that file to your project directory.

In the code chunk below, load the readr package, read the file in and assign it to the name `data`.

```{r}



exists("data")
```


## Examine data

How many rows and columns does `data` have?

```{r}

```

Get the last 10 rows and last 2 columns of `data`

```{r}

```

Get the `content` and `session_id` variables from `data`

```{r}

```


## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much) 
scale by replacing the "x" below with your response:

```{r}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:



If you like, you can post these other comments, feedback, or reflections in the 
message you post to #homework in Slack to share what you've done.