---
title: "Week 1 - Tutorial"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First, let's install and load ggplot2 

We'll do so by running the following line of code; click the green arrow to the
right to run the code!

```{r}
install.packages("ggplot2")
```

Next, we'll "load" ggplot2, or check it out for use in our current analysis / R 
session. Run this next chunk the same way as the first:

```{r}
library(ggplot2)
```

## Print a built-in dataset

Next, simply run msleep to view a dataset built-in to R:

```{r}
msleep
```

What do you notice? What do you wonder? Consider viewing additional rows by clicking
the numbers at the bottom of the table; or more rows by clicking the black right arrow 
at the top.

Add a few thoughts on what you notice and what you wonder after the dashes below!
You can add additional dashes, if needed!

- 
- 
- 

## Run code to a plot

Here, we will run code to create our first plot. 

The ggplot2 package has a function, ggplot(), that we will use.

This function takes arguments for: a) what variables in a dataset correspond to 
different aesthetic features of a graph, like an x- and y-axis, and b) how the data
is represented.

Below, bodywt and sleep_total correspond to the x- and y-axis, respectively, and 
the values are represented by a point.


```{r}
ggplot(msleep, aes(x = bodywt, y = sleep_total)) +
  geom_point()
```

Nice job!

Plots can be constructed layer-by-layer; here, let's add the conservation status
of the mammals by color.

See what the conservation statuses represent here: 
https://en.wikipedia.org/wiki/Category:Biota_by_conservation_status

```{r}
ggplot(msleep, aes(x = bodywt, y = sleep_total, color = conservation)) +
  geom_point()
```

There are many graphs you can create, from the simple to the complex!

For example, we can quickly look at the distribution of the sleep_total variable
with a density plot:

```{r}
ggplot(msleep, aes(x = sleep_total)) +
  geom_density()
```

## Create your own plot!

Now, create your own plot, using the following two code chunks as a foundation or starting 
points. Look above at the variables in the msleep dataset (where you printed the data) for a 
reminder of what the dataset includes!

First, can you create a density plot using a different variable (other than sleep_total)?

Try it out below:

```{r}
ggplot(msleep, aes(x = )) +
  geom_density()
```

Next, can you create a different scatterplot; or a version of one? Try it out by adding
different variables for the x, y, and color arguments below:

```{r}
ggplot(msleep, aes(x = , y = , color = )) +
  geom_point()
```

## fin

Great job! Once you've finished your work, click "Knit" at the top to render a 
report that you can share; this is how you'll submit homework for class!

:clap:
