---
title: "Homework Week 9 - From Soup to Nuts"
output: html_document 
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background

This homework is different in nature than those to this point; it is more open-
ended in nature, and it asks you to step back and to synthesize and apply all of
the great work you have done so far in this course.

There are three requirements:

1.  Load a data set of your choosing. This can be data that you have already
    collected, or, it can be a publicly available data set (regardless of how
    you load it). In addition, we have a few example data sets that you can use;
    all are available in this folder on GitHub:
    <https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/tree/main/data>

These are briefly described below:

  - Twitter data on the \#rstats hashtag:
      - rtweet-on-twitter.csv

  - Posts from K-12 districts and schools on Facebook from 2019:
      - districts-schools-fb-2019.csv

  - The tidykids data set; described in HW5:
    <https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-5.Rmd>
      - tidykids.csv

  - Two files related to states' adoption of the NGSS
      - ngss-adoption-states.xlsx
      - ngss-adoption.xlsx

  - Four files related to a study of undergraduate students' interest in CS1
    (introductory computer science courses); described in HW4:
    <https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-4.Rmd>
      - answer\_export.csv
      - twilio\_data.csv
      - undergrad\_data.csv
      - database\_data.csv

Again you can use any data set you find interesting. A key for us is that it is
not a built-in data set (i.e., the mpg or storms data sets that are built-in to
R); we want to see that you can identify, access/load, and use a data set of
your choosing. You can reach out to us with any questions at all about whether a
data set you have is suitable; even smaller data sets are fine with us!

2.  Please create a visualization of one or more of the variables in your data.
    Focus on telling a story about your data; this can be done through attention
    to the the labels you use as well as other features of the plot - what geoms
    or features you use, how you use colors or themes, etc.

3.  Please create a table representing your data or a summary of your data; a
    simple table is satisfactory. Consider summary statistics that you calculate
    yourself or do so using a package from HW8
    (<https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-8.Rmd>),
    correlation tables, or in any other way. Please use the kable package
    (described in HW8) to format your table; it is okay if you do not add any
    options to style your table like in HW8, but, the reach for this week is to
    do this.

You can consider the kableExtra package:
<https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html>

4.  Add a brief (3-4 sentence) description of the work you did. You can add this
    above, below, or between the visualization and table you create.

5.  There is also a new element that we would like to add to this assignment,
    that is relatively minor, but important to know about

Rmarkdown gives you the ability to fine tune what ends up in your final document
using what are called chunk options.

Chunk options are parameters that you can put into the chunk header to control
how and whether the output of your code end up in the final document. For
example:

``` {r, include=FALSE}

```

In the chunk above I added the chunk option `include=FALSE` to tell R not to
include that chunk in my document, although what that means is a bit more
nuanced. There are many chunk options that you can use to control what your
output looks like. The most relevant for our purposes here are `include`,
`results`, `echo`, `warning`, and `message`. The default value for all of these
is `TRUE` (except `results`) but you can change the behavior of your document in useful ways by changing them to `FALSE`

  - `include=FALSE` will hide the code itself as well as the results from the
    document.
  - `results='hide'` will hide the results from the document but keep the code.
  - `echo=FALSE` will hide the code from the document but keep the results.
  - `warning=FALSE` will hide warnings generated by your code but not the code
    or results.
  - `message=FALSE` will hide messages generated by your code but not the code
    or results.

For a further explanation of what these chunk options do and how you use them,
we have prepared an explanation video which is here:

<https://tennessee.zoom.us/rec/share/wCxEUXjYysY5Zb2mjpyNUMzP6W-rgyf9bOA6scu-tVOggeR6TQEXW3gvhG9R5Eov.FLxCdBmt3fgxLgiy>

For this assignment, we would like you to use these chunk options to make your
document show only your main output and not the code or any warnings or
messages. So your final document should only have the text and headings already
here, your plot, your output table, and your explanatory prose, but no code or
other warnings or messages. If you have questions about what this means please 
ask us on slack.

Please add your work in code chunks and text below.


## My work



## fin

Render and submit:

  - Submit the .html file you used to render a report to Canvas - Upload the
    .Rmd file you rendered to the \#homework channel in Slack. One difference
    from last week: Please post a comment, feedback, or reflection below *as
    well as to Slack when you post your homework*.

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much)
scale by replacing the "x" below with your response:

``` {r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:


Important note: Please post your comment(s), feedback, or reflections in Slack
when you share your Rmd file!
