---
title: "HW Week 5 - Introduction to Data Viz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background 

For this homework, we are going to be working with the Experience Sampling
Method - ESM - data that we used in class.

Here's a bit of an overview and a reminder of this dataset. The database
contains responses, corresponding question numbers, unique identifiers for the
survey and for the item level responses, and the course assignment that each
survey corresponds to. What it does not have are unique identifiers of the
person who sent it, i.e.:

- their phone number 
- the date and time when it was sent
- and, if we wanted later, other information, such as information about their major

That's where the Twilio (ESM) data file comes in it does have that information,
and importantly, it also uses the same unique identifiers for the ESM responses. 

It also has some junk in it that we *don't* want, like the messages
where students initiated but didn't take the survey.

To provide just a bit more context, students answered our five ESM survey items \~11 times
each, with some doing so as many as 18 times. 

So, it might be interesting to look at the five survey questions, and see what 
 average responses were for each question for each student.

In class we went over getting the mean by survey question overall, but this time we
want to know how each person responded on average to each item. There's \~75
people in this dataset, and, again five survey items.

**So, just to sum up, we have around 75 students each responding around 11 times 
to five questions. What we'd like to get is a summary data table that's 75 rows 
and 5 columns, with each entry being each person's average response for each of the 
five questions.** 

There's a lot here, and if you have questions about any of this, please message us
over in the #questions channel on Slack. You'll note that this is entirely data 
tidying/processing, but is very much the kind of thing that you may wish to do as 
the descriptive part of an analysis for a research project.

This task will involve a number of steps that we'll tackle one at a time, then at the
end we can put everything together and you will (maybe?) marvel at what you've done.

## Downloading the data and saving them to the data directory

```{r}

```

## fin

You know the drill; render and please submit:

- Submit the .html file you used to render a report to Canvas
- Upload the .Rmd file you rendered to the #homework channel in Slack.

One difference from last week: Please post a comment, feedback, or reflection
below *as well as to Slack when you post your homework*.

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much) 
scale by replacing the "x" below with your response:

```{r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:


Important note: Please post your comment(s), feedback, or reflections in Slack when you share your Rmd file!