---
title: "Week 1 - Tutorial"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## First, let's install and load ggplot2 

We'll do so by running the following line of code. This line of code, though, is 
a bit different from most: it installs a new R "package" with specific, additional 
functionality. Installing R packages is very common. The reason it is different from
most code, though, is you typically only want to run it once - after that, the package
is installed on your computer, and you don't need to run it again. For that reason,
we've commented out this line of code below. You will just have to remove that 
comment symbol and then click the green arrow to the right to run the code!

```{r}
# install.packages("ggplot2")
```

Next, we'll "load" ggplot2, or check it out for use in our current analysis / R 
session. Run this next chunk the same way as the first:

```{r}
library(ggplot2)
```

## Print a built-in dataset

Next, simply run msleep to view a dataset built-in to R:

```{r}
msleep
```

What do you notice? What do you wonder? Consider viewing additional rows by clicking
the numbers at the bottom of the table; or more rows by clicking the black right arrow 
at the top.

Add a few thoughts on what you notice and what you wonder after the dashes below!
You can add additional dashes, if needed!

- 
- 
- 

## Run code to a plot

Here, we will run code to create our first plot. 

The ggplot2 package has a function, ggplot(), that we will use.

This function takes arguments for: a) what variables in a dataset correspond to 
different aesthetic features of a graph, like an x- and y-axis, and b) how the data
is represented.

Below, bodywt and sleep_total correspond to the x- and y-axis, respectively, and 
the values are represented by a point.

```{r}
ggplot(msleep, aes(x = bodywt, y = sleep_total)) +
  geom_point()
```

Nice job!

Plots can be constructed layer-by-layer; here, let's add the conservation status
of the mammals by color.

See what the conservation statuses represent here: 
https://en.wikipedia.org/wiki/Category:Biota_by_conservation_status

```{r}
ggplot(msleep, aes(x = bodywt, y = sleep_total, color = conservation)) +
  geom_point()
```

There are many graphs you can create, from the simple to the complex!

For example, we can quickly look at the distribution of the sleep_total variable
with a density plot:

```{r}
ggplot(msleep, aes(x = sleep_total)) +
  geom_density()
```

## Create your own plot!

Now, create your own plot, using the following two code chunks as a foundation or starting 
points. Look above at the variables in the msleep dataset (where you printed the data) for a 
reminder of what the dataset includes!

First, can you create a density plot using a different variable (other than sleep_total)?

Try it out below:

```{r}
ggplot(msleep, aes(x = )) +
  geom_density()
```

Next, can you create a different scatterplot; or a version of one? Try it out by adding
different variables for the x, y, and color arguments below:

```{r}
ggplot(msleep, aes(x = , y = , color = )) +
  geom_point()
```

## Reach!

Completed the above? Try for a "reach" in one of three ways:

1. Add a line of best fit to one of the scatterplots you created above in the
blank codechunk below.

To learn how, check out this excellent cheat sheet: https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf

Or consult this chapter on visualizing data with ggplot2: 
https://r4ds.had.co.nz/data-visualisation.html

```{r}

```

2. Create a plot of your choice using a *different* dataset built in to ggplot2.

To see available datasets, run the following code chunk:

```{r}
data(package = "ggplot2")
```

To load the data, simply type its name. Create your plot in the code chunk below:

```{r}

```

3. Create a plot using a *dataset of your choice*. There are a number of datasets
built into R; to see all of those on your machine, run the following code chunk
(warning - if you've installed a number of packages already, you may have a lot!):

```{r}
data(package = .packages(all.available = TRUE))
```

Create your plot below:

```{r}

```

## fin

Great job! Once you've finished your work, click "Knit" at the top to render a 
report that you can share; this is how you'll submit homework for class! 

Please submit this rendered HTML file in both a) canvas and b) the #homework-week-1
channel in Slack.

:clap: :clap: :clap:

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much) 
scale by replacing the "x" below with your response:

```{r}
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:
