---
title: "Homework Week 9 - From Soup to Nuts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background 

This homework is different in nature than those to this point; it is more open-
ended in nature, and it asks you to step back and to synthesize and apply all of
the great work you have done so far in this course. 

There are three requirements:

1. Load a data set of your choosing. This can be data that you have already collected,
or, it can be a publicly available data set (regardless of how you load it). In addition, 
we have a few example data sets that you can use; all are 
available in this folder on GitHub: https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/tree/main/data

These are briefly described below:

- Twitter data on the #rstats hashtag:
  - rtweet-on-twitter.csv

- Posts from K-12 districts and schools on Facebook from 2019:
  - districts-schools-fb-2019.csv

- The tidykids data set; described in HW5: https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-5.Rmd
  - tidykids.csv

- Two files related to states' adoption of the NGSS
  - ngss-adoption-states.xlsx
  - ngss-adoption.xlsx

- Four files related to a study of undergraduate students' interest in CS1 (introductory computer science courses); described in HW4: https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-4.Rmd
  - answer_export.csv
  - twilio_data.csv
  - undergrad_data.csv
  - database_data.csv

Again you can use any data set you find interesting. A key for us is that it is not a built-in data set (i.e., the mpg or storms data sets that are built-in to R); we want to see that you can
identify, access/load, and use a data set of your choosing. You can reach out to us with any questions at all about whether a data set you have is suitable; even smaller data sets are fine
with us!

2. Please create a visualization of one or more of the variables in your data. Focus on 
telling a story about your data; this can be done through attention to the the labels you use
as well as other features of the plot - what geoms or features you use, how you use colors
or themes, etc. 

3. Please create a table representing your data or a summary of your data; a simple table is
satisfactory. Consider summary statistics that you calculate yourself or do so using a package
from HW8 (https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/blob/main/homework/homework-week-8.Rmd), correlation tables, or in any other way. Please use the kable package (described in HW8) to format your table; it is okay if you do not add any options to style your table like in HW8, but, the reach for this week is do this this. 

You can consider the kableExtra package: https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

4. Finally, add a brief (3-4 sentence) description of the work you did. You can add this above, 
below, or between the visualization and table you create. 

Please add your work in code chunks and text below.

## My work



## fin

Render and submit:
- Submit the .html file you used to render a report to Canvas - Upload the .Rmd
file you rendered to the #homework channel in Slack.
One difference from last week: Please post a comment, feedback, or reflection
below *as well as to Slack when you post your homework*.

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much)
scale by replacing the "x" below with your response:

```{r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:


Important note: Please post your comment(s), feedback, or reflections in Slack
when you share your Rmd file!
