---
title: "Homework Week 14 - Network and Text Analysis"
output: html_document 
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

In this homework, we'll carry out a text analysis. For reference, the slides from class are here:

XX

A relevant tutorial is here:

XX

## Reach 1

For this reach, use the imputed data sets you created above to fit a regression model, and pool the estimates and generate a summary table.

```{r}

```

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much)
scale by replacing the "x" below with your response:

``` {r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:

Important note: Please post your comment(s), feedback, or reflections in Slack
when you share your Rmd file!
