---
title: "Homework Week 14 - Network and Text Analysis"
output: html_document 
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

In this homework, we'll carry out a text analysis. For reference, the slides from class are here:

https://making-data-science-count.github.io/s21-intro-to-data-sci-methods-in-ed/slides/presentations-week-14.html#1

A relevant resource for the tidytext package is here

https://www.tidytextmining.com

We'll focus on term frequencies, though you'll have a chance to carry out a sentiment analysis, too, for a reach.

## Term frequencies

First, download the file aera-tweets-2019-2020-2021.csv from the repository. It is available
here: https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/tree/main/data/aera-tweets-2019-2020-2021.csv. Save it to the directory you're using for this project and
read this file in to R using the read_csv() function loaded from the tidyverse in the next code chunk.

```{r}
d <- read_csv("../data/aera-tweets-2019-2020-2021.csv")

d
```

Next, load (and, if you haven't at this point, install) the tidytext package.

Then, use the unnest_tokens() function to "unnest" the terms in the "text" column. 

Save the result to a new object (preferably one with a different name than the name
you used when you read in the data).

If you need help, consider the documentation for unnest_tokens here: 
https://juliasilge.github.io/tidytext/reference/unnest_tokens.html

```{r}
library(tidytext)

dd <- d %>% 
  unnest_tokens(term, text)
```

What terms are most frequent? To answer this question, use the count() function, counting
up the values of the column in your data set representing the terms. You may find the
sort argument for count handy; check out ?count to see how to use it.

```{r}
dd %>% 
  count(term, sort = TRUE)
```

## Reach 1

For this reach, use the imputed data sets you created above to fit a regression model, and pool the estimates and generate a summary table.

```{r}

```

## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much)
scale by replacing the "x" below with your response:

``` {r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:

Important note: Please post your comment(s), feedback, or reflections in Slack
when you share your Rmd file!
