---
title: "Homework Week 12 - Functions"
output: html_document 
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

In this homework, we'll extend what we discussed in this week's class on a) writing
functions and b) strategies for applying a function multiple times.

The slides for this week are here:
https://making-data-science-count.github.io/s21-intro-to-data-sci-methods-in-ed/slides/presentations-week-12.html#1

## Functions

As discussed in class, functions take some input and return some output. There are many kinds 
of functions, and some nuance around this definition, but, generally, it describes the core of what 
functions do within R---and within other programming languages!

In class, we presented a "skeleton" of a function. Below, we make that skeleton even more
of one - we even removed its name! 

For this part of the homework, imagine that the R Core Team (who developed and maintains
R, but not R packages) *forgot* to write a function for calculating the mean of some values.

If necessary, for an intuitive description of how to calculate the mean, see this webpage: https://www.mathsisfun.com/mean.html#:~:text=How%20to%20Find%20the%20Mean,sum%20divided%20by%20the%20count.

In your function, you'll need to write three things:

1. The name of your function (something other than mean, for reasons we'll mention momentarily)
2. What inputs your function takes
3. What operations, or steps, to take to transform the input 

You can do this below. One important note - the last line of your function will be
what is returned by the function (by default). It is critically important that the last
line of your function does not include an assignment operator. Check the slides for an
example of this.

```{r}
___ <- function(___) {
  ___
}
```

Once you've written your function, you're free to test (and use!) it. 

Below, first, the use of the mean function is demonstrated using the storms dataset:

```{r}
library(tidyverse)

mean(storms$wind)
```

Note how the $ operator is a way of indexing (similar to selecting with the `select()` function)
a variable in a data frame. It is slightly different from select() in that select returns a data frame
including the specified variables, whereas the $ returns only that single variable: technically,
it returns a vector (for that single variable).

Below, check that your function returns the same result as the mean function built-in to R. If they are
identical, proceed! If not, consider why there may be differences, and work to de-bug your function.

```{r}

```

## Iteration

Next, we'll iterate with the function we wrote. First, read the tidykids dataset (directly from the URL
to it on GitHub), naming the dataset d (for data; you can, of course, name it something
different if you like!). 

```{r}
d <- read_csv("https://github.com/making-data-science-count/s21-intro-to-data-sci-methods-in-ed/raw/main/data/tidykids.csv")
```



## Self-assessment and reflection

Respond to the following three questions on a 1 (not at all) to 5 (very much)
scale by replacing the "x" below with your response:

``` {r, reflection}
x = NULL
tibble::tribble(
  ~question,                                   ~response,
  "How challenging was this homework?",        x,
  "How interesting was this homework to you?", x,
  "How valuable was this homework to you?",    x
)
```

Include any other comments, feedback, or reflections on this homework below:


Important note: Please post your comment(s), feedback, or reflections in Slack
when you share your Rmd file!
