---
title: "Week 10 - Modeling Data" 
subtitle: ""
author: "Joshua Rosenberg and Alex Lishinski"
date: "March 15, 2021"
output:
  xaringan::moon_reader:
    css: [theme.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE)
```

# Welcome!

Welcome to *week 10*!

```{r echo = FALSE, out.width = "70%"}
```

**Record the meeting** 

```{r, include = TRUE, echo = FALSE}
library(here)
library(tidyverse)
```

---

# Breakout rooms!

Starting with XXX



---

**Record the meeting** 

### Review of last week's class

- From Soup to Nuts: Carrying out a complete analysis

- Exam 2

---

### Homework highlights

```{r echo = FALSE, out.width = "90%"}

```

Alex to add

---

### Exam recap

Alex to add

---

### Mid-semester feedback 

Alex to add

---

### This week's topics

**Overview**

A. Final project presentations

B. A buffet of models

---

### A. Final project presentations

* Thank you for adding your ideas to the final project brainstorm! 

  * https://docs.google.com/presentation/u/3/d/1KWU5bhxZmV63vkNtQNxHo-2YI_iYJmSW2oOZ_jtFeP0/edit#slide=id.p

* Today, each of you will briefly (1 min. or less) present on your final project idea

* We will each provide feedback via Jamboard
  * https://jamboard.google.com/d/1S6K3ED_jvCS5b-GP3wfk5S3o6g4Buj0wgq6fTlmUY2w/edit?usp=sharing

---

### B. A buffet of models

There are a number of ways to understand variables about which you have data and the
relationships between them.

One way is to create a **model**, a simplified _representation_ of your data that
can be informative to you (and others) about your data - and, maybe, what your data
represents. 

From this broad definition, models can take many different forms:

- A sample statistic (e.g., a _mean_ of a variable)
- A relationship describing how two variables co-vary (e.g., a bivariate _correlation_)
- A linear regression model
- . . . (what models are common in your field?)

---

### B. A buffet of models

One of the benefits of modeling your data within R is that many R packages share a 
common modeling syntax, or interface: the formula syntax.

This code represents the regression of `hp` upon `mpg`:

```{r, eval = FALSE}
mpg ~ hp
```

This code often corresponds to the underlying mathematical/statistical equation:

```{r, echo = FALSE}
m1 <- lm(mpg ~ hp, data = mtcars)
equatiomatic::extract_eq(m1)
```

---

### B. A buffet of models

Today, we'll focus on the linear regression model, but will also touch on the following:

- *t*-test
- ANOVA
- generalized linear model (i.e., Poisson or Logistic Regression)
- multi-level (or hierarchical linear) model

---

### B. A buffet of models

There is a _lot_ we can do with a linear regression model!

```{r, warning = FALSE, message = FALSE}
d <- read_csv("https://raw.githubusercontent.com/data-edu/dataedu/master/data-raw/wt01_online-science-motivation/processed/sci_mo_processed.csv")

d
```

---

### B. A buffet of models

Estimating a model; seeing the result:

```{r, warning = FALSE, message = FALSE}
lm(FinalGradeCEMS ~ TimeSpent_hours, data = d)
```
---

### B. A buffet of models

Saving the output to an _object_ and printing a summary of the results

```{r, warning = FALSE, message = FALSE}
m1 <- lm(FinalGradeCEMS ~ TimeSpent_hours, data = d)
summary(m1)
```

---

### B. A buffet of models

Making the model more complex

```{r, warning = FALSE, message = FALSE}
m2 <- lm(FinalGradeCEMS ~ TimeSpent_hours + int + Gender, data = d)
summary(m2)
```


---

### B. A buffet of models

```{r}

lm()
```

---

### B. A buffet of models

*t*-test

```{r}

```

---

### B. A buffet of models

ANOVA

```{r}

```

---

### B. A buffet of models

Multi-level model

```{r}

```

---

### Live coding

Let's head over to the following file for a demonstration: Week 8 demo

---

# Logistics

**This week**

* Homework 10: Available tomorrow by noon tomorrow; **Due by Thursday, 4/1**

* Reading:
  *

---

# Final Project

* [Final project](https://making-data-science-count.github.io/s21-intro-to-data-sci-methods-in-ed/assignments-final-projects.html)

* [Slide deck to edit this week](https://docs.google.com/presentation/d/1KWU5bhxZmV63vkNtQNxHo-2YI_iYJmSW2oOZ_jtFeP0/edit?usp=sharing)
  * Must be logged in to UTK email/account
  
---

### Random

* Do you have an interest in a class on social network analysis (more of a general theoretical and methodological approach that can be brought to bear on the analysis of face-to-face and digital networks) and the analysis of social media data? If so, please let me know.

---

### Wrapping up

In your base group's Slack channel:

- What is one thing you learned today?
- What is something you want to learn more about? 
- Share your feelings in GIF form!

We really appreciate being able to see these reactions and get this feedback!
