---
title: "Week 12 - Functions and Iteration" 
subtitle: ""
author: "Joshua Rosenberg and Alex Lishinski"
date: "April 8, 2021"
output:
  xaringan::moon_reader:
    css: [theme.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", message = FALSE)
```

# Welcome!

Welcome to *week 11*!

```{r echo = FALSE, out.width = "70%"}
```

**Record the meeting** 

```{r, include = TRUE, echo = FALSE}
library(here)
library(tidyverse)
```

---

# Breakout rooms!

Starting with whomever has the most plans for summer . . .

- What aspects of the model formulas in R do you feel like you don't understand yet after reading the chapter?

Prepare one-three responses to each of the above questions to share with the whole class!

https://www.tmwr.org/base-r.html

---

## A recap of last week (on modeling)

- A model is a simplification (and a summary) of your way
- A common type of model is a regression model, aka a linear regression model (or a linear model)


This code represents the regression of `hp` upon `mpg`:

```{r, eval = FALSE}
mpg ~ hp
```

This code often corresponds to the underlying mathematical/statistical equation:

```{r, echo = FALSE}
m1 <- lm(mpg ~ hp, data = mtcars)
equatiomatic::extract_eq(m1)
```

---

## A recap of last week (on modeling)

- A linear model can help you learn how one or more _independent variables_ (or, _x_ variables) relate to one _dependent variable_ (a _y_ variable)
- It is common to specify a number of models, and to compare them (commonly based on how much of the variation in the dependent variable is accounted for by relationships with the _x_ variable(s))
- the `lm()` function is a great tool for specifying relatively simple linear regression models, but it can be extended in a number of powerful ways
- R has a number of tools for interpreting and presenting the output of models

---

## Checking-in on final projects

- Overall feedback: Good work!
- And, generally, please consider a) the scope of your project and b) the level of detail in your plans
- We want you to do a small(er) number of things well - and in a way that positions you for your next project
- Please revise your plan in response to our feedback over the next week 

---

## Homework highlights

A brief description of chunk options!

---

### Topics for today

**Record the meeting** 

A. Functions
B. Iteration (or, _applying_ functions)
(C. On creating maps using ggplot2)

---

### A. Functions

A function is a collection of code that:

- takes one or more inputs (most commonly in R, data!)
- and produces one or more forms of output (often, your data---transformed!)

You _already_ use functions all of the time:

```{r}
mpg
```

---

### A. Functions

**`select()` is a function**

```{r}
mpg %>% 
  select(model, displ, cyl)
```

---

### A. Functions

**`select()` and `filter()` are functions**

```{r}
mpg %>% 
  select(model, displ, cyl) %>% 
  filter(cyl == 6)
```

---

### A. Functions

There are all kinds of functions:

```{r}
mpg %>% 
  summarize(mean_cty = mean(cty),
            mean_hwy = mean(hwy))
```

```{r}
ten_mpg_values <- c(13, 63, 23, 43, 23, 33, 42, 34, 21, 23)
mean(ten_mpg_values)
```

---

### A. Functions

You can write your own functions!

Suppose we want to write a function to _standardize_ the `cty` variable to have _M_ = 0 and _SD_ = 1;
presently, its *M* and *SD* are:

```{r}
mpg %>% 
  summarize(mean_cty = mean(cty),
            sd_hwy = sd(hwy))
```
---

### A. Functions

(In this case, there _is_ an existing function, but it has some quirks, including, importantly, returning a _matrix_, rather than a vector/"a column")

So, let's write our own. Here is a template, with two "blanks" represented by "___":

```{r, eval = FALSE}
standardize_a_variable <- function(___) {
  ___
}
```

---

### A. Functions

**A not very useful function!**

```{r}
standardize_variable <- function(variable) {
  variable
}
```

```{r}
mpg %>% 
  mutate(cty_std = standardize_variable(cty)) %>% 
  summarize(mean_cty_std = mean(cty_std),
            sd_cty_std = sd(cty_std))
```

---

### A. Functions

**A useful `standardize_variable`**

```{r}
standardize_variable <- function(variable) {
  variable <- variable - mean(variable) # transforms variable to have M = 0
  variable <- variable / sd(variable) # transforms variable to have SD = 1
  variable
}
```

```{r}
mpg %>% 
  mutate(cty_std = standardize_variable(cty)) %>% 
  summarize(mean_cty_std = mean(cty_std),
            sd_cty_std = sd(cty_std))
```

---

### A. Functions

**Let's double-check that the mean is practically equal to 0** (by rounding to precision to three decimal points)

```{r}
mpg %>% 
  mutate(cty_std = standardize_variable(cty)) %>% 
  summarize(mean_cty_std = mean(cty_std),
            sd_cty_std = sd(cty_std)) %>% 
  mutate(mean_cty_std_rounded = round(mean_cty_std, 3))
```

---

### A. Functions

We can add an argument to a function to modify how it works.

```{r}
standardize_variable <- function(variable, remove_na_values = FALSE) {
  variable <- variable - mean(variable, na.rm = remove_na_values)
  variable <- variable / sd(variable, na.rm = remove_na_values)
  variable
}

```

---

### A. Functions

What if we wanted to scale the variables cty, hwy, and cyl? Imagine that drv has a missing (`NA`) value.

```{r}
mpg %>% 
  mutate(cty_std = standardize_variable(cty),
         hwy_std = standardize_variable(hwy),
         cyl_std = standardize_variable(cyl, remove_na_values = TRUE)) %>% 
  select(cty_std, hwy_std, cyl_std, everything()) # bring the new variables to the beginning of the data frame
```

---

### A. Functions

In summary:

- You already use functions all of the time
- You can write your own functions that take one or more types of input and return output
- The functions that you are using within R were written by other people!
- https://github.com/tidyverse/dplyr/blob/master/R/select.R
- https://github.com/SurajGupta/r-source/blob/master/src/library/stats/R/median.R
- https://github.com/jrosen48/konfound
- https://github.com/data-edu/tidyLPA
- If you find yourself copying and pasting the same code, it may be worthwhile to encapsulate your code within a function (more on this in a moment!)

---

### B. Iteration

Iteration is another name for your computer carrying out some step(s) multiple times.

Iteration is helpful when, ven after writing a function, you find yourself copying and pasting the same code (with modifications)

---

### B. Iteration

Another way of writing the above code in which we are scaling multiple variables:

```{r}
mpg %>% 
  mutate_at(vars(cty, hwy, cyl), standardize_variable) %>% 
  select(cty, hwy, cyl, everything()) # bring the transformed variables to the beginning of the data frame
```
---

### B. Iteration

Iteration can be helpful when you want to apply a function multiple times.

For example, one of us recently needed to download 14 surveys for a teacher professional development-focused
research project, https://megabitess.org!

There is a great package, qualtRics, which can help with this, but it's tedious to have to download the surveys one-by-one.

The map functions can help with this. 

Let's hop over to `qualtrics-example.R`

---

### C. Mapping with ggplot2

A brief introduction for those interested, focused on the sf R package:

https://joshuamrosenberg.com/post/2020/06/08/basic-sf-functionality-for-analyzing-and-plotting-geospatial-data/

---

# Logistics

**This week**

* Homework 12: Available tomorrow by noon; **Due by Thursday, 4/15**

* Reading: 
* Longitudinal analysis: https://datascienceineducation.com/c10.html

---

## Schedule

- The product for your final project and a recording that will serve as your presentation of it are both due by the end of the day on May 5
- *There is no portfolio!*
- Exam 3 will be available April 15, due before class on April 22
- The revised data ethics statement is due April 29 (*changed*)
- The curating a resource assignment is due by the same date/time as the final project - May 5
---

# Assignment updates

* [Final project](https://making-data-science-count.github.io/s21-intro-to-data-sci-methods-in-ed/assignments-final-projects.html)
* Responding to feedback
* We recommend having starting in earnest within the next one-two weeks
* [Curating a data science resource](https://making-data-science-count.github.io/s21-intro-to-data-sci-methods-in-ed/assignment-curating-a-data-science-resource.html)

---

### Random

* Do you have an interest in a class on social network analysis (more of a general theoretical and methodological approach that can be brought to bear on the analysis of face-to-face and digital networks) and the analysis of social media data? If so, please let us know.

* Are you interested in a graduate-level certificate in educational data science? 
* https://docs.google.com/document/d/e/2PACX-1vRhJTuCQfpEx9uZl57pucjyr_quIR9Vv5ZZdxvu4GSrdD5lkIQyUTsWX5NyuHiPivvOMPtkLmoLoi1X/pub
---

### Wrapping up

In your base group's Slack channel:

- What is one thing you learned today?
- What is something you want to learn more about? 
- Share your feelings in GIF form!
